From Freebase to Wikidata: The Great Migration

### 2015-10-17 paper.tex
Added exemplary works in the introduction.

Large Web-based knowledge bases that make their data available
under free licenses in a~machine-readable form
have become central for the data strategy of many projects and organizations.
They find applications in areas as diverse as Web search,
natural language annotation, or translation.
\todo{add references to papers with examples}

>>>>

Large Web-based knowledge bases that make their data available
under free licenses in a~machine-readable form
have become central for the data strategy of many projects and organizations.
They find applications in areas as diverse as Web search,
natural language annotation, or translation.
Exemplary works are those of West \emph{et~al.}, who have proposed~\cite{west2014kb} a~way to
leverage existing Web search based question-answering technology to
fill in the gaps in knowledge bases in a~targeted way
or those of Gesmundo and Hall~\cite{gesmundo2014kb}, who have trained
a~syntactic parser paradigm that learns from large scale knowledge bases.
